Multisymplectic observables and higher Courant algebroids

### 2024-02-21 msgauge-Caprarola.tex
Updating slides for Caprarola.

%+----------------------------------------------------------------------------+
%| SLIDES: 
%|
%| Contents:	- 60 minutes, 
%|
%| Author: Antonio miti
%| Place: Caprarola, VT
%| Date: 2/3/24
%+----------------------------------------------------------------------------+

%- D0cum3nt ----------------------------------------------------------------------------------------------
\documentclass[10pt]{beamer}

@@

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[fragile]{A \emph{pentagonal} diagram in symplectic geometry}
	Given a \alert{symplectic mfd.} $(M,\omega)$ ...
	\vfill
	\begin{center}
		\includestandalone[width=.95\textwidth]{Pictures/Frame_Embedding_Diagram_symplectic}
	\end{center}
	\vfill
	\begin{minipage}[t][8.5em][t]{\textwidth}
		\begin{itemize}
			\only<1-3>{
			\item<1-> \alert<1>{... there is a naturally associated Poisson algebra ...}
			\item<2-> \alert<2>{... and also a (standard twisted) Lie Algebroid}.
			\item<3-> A Lie algebroid is a "controlled" $\infty$-dimensional Lie algebra given (in this case) by
			\begin{displaymath}
					\left[\binom{x_1}{f_1},\binom{x_2}{f_2}\right]_\omega
					~=~
					\binom{[x_1,x_2]}{x_1(f_2)-x_2(f_1)-\omega(x_1,x_2)}
				\end{displaymath}
			}
			\item[]<4->
				\quad\\
				\begin{thmblock}[There exists an embedding of Lie algebras.]
					\begin{displaymath}
						\begin{tikzcd}
							\Psi~:&[-1em] C^{\infty}(M)_\omega \ar[r,"\Psi"]& \Gamma(TM\oplus \mathbb{R})_\omega
							\\[-2em]
							& f \ar[r,mapsto] & \binom{\mathscr{v}_f}{f}
						\end{tikzcd}		
					\end{displaymath}
				\end{thmblock}
		\end{itemize}
	\end{minipage}
\end{frame}
\note{}
%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[fragile]{A \emph{pentagonal} diagram in symplectic geometry}
	%
Consider two \alert{gauge-related} symplectic mfd. $(M,\omega)$ and $ (M,\widetilde{\omega})$.
	%
	\begin{center}
			\includestandalone[width=.8\textwidth]{Pictures/hyb-Frame_BigDiagram_symplectic}
	\end{center}
		\vfill
	\begin{minipage}[t][8em][t]{\textwidth}
		\begin{itemize}
			\only<3-4>{
				\item<3-> There is a natural \alert<3>{isomorphism in the Lie Alg.oids category} \emph{($B$-transformation)}
					\begin{displaymath}
						\binom{x}{f} \mapsto \binom{x}{f-\iota_x B} ~.
					\end{displaymath}~.
				\item<4-> It descends to an \alert<4>{isomorphism of Lie algebras}.
			}
			\only<6-8>{
				\item<6-> \vspace{-2em}Consider an infinitesimal \alert<6>{Hamiltonian group action} $\mathfrak{g}\circlearrowleft M$ w.r.t. both $\omega$ and $\tilde{\omega}$.
				\item<7-> let be $f:\mathfrak{g} \to C^\infty(M)_\omega$ and $\tilde{f}:\mathfrak{g} \to C^\infty(M)_{\tilde{\omega}}$ two comoment map s.t.
				\begin{displaymath}
					\tilde{f}(\xi) = f(\xi) - \iota_{\underline{\xi}}B
				\end{displaymath}
				}
			\item[]						
		\end{itemize}
	\only<2>{
		\vspace{-.75em}
		\begin{center}
		\tcbox[enhanced,frame hidden,borderline={0.5pt}{0pt}{red,dashed}]{	
			\alert{
			\faQuestionCircle \qquad
				{How can we compare the two \emph{observables} algebras?}
			\qquad \faQuestionCircle		
			}
		}
		\end{center}
	}
	\only<5>{
		\vspace{-.75em}
		\begin{center}
		\tcbox[enhanced,frame hidden,borderline={0.5pt}{0pt}{red,dashed}]{	
			\alert{
			\faQuestionCircle \qquad
				{How can we close the left-hand side?}
			\qquad \faQuestionCircle		
			}
		}
		\end{center}
	}
	\only<8->{
		\vspace{-.75em}
		\tcbset{colback=white,
		colbacktitle=white,
		colframe=red!70!black,
		boxrule=1pt,
		colupper=red!70!black,
		arc=15pt,
		}
		\begin{tcolorbox}[enhanced,frame hidden,borderline={0.5pt}{0pt}{blue}]
			\color{blue}{
			\textbf{Lemma}: The central pentagon commutes!
			}
		\end{tcolorbox}
	\vfill
	}
	\end{minipage}	
\end{frame}
%-------------------------------------------------------------------------------------------------------------------------------------------------

@@

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[fragile]{TODO}
	Why we can't directly relate the two Poissons?
\end{frame}
%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[fragile]{A \emph{pentagonal} diagram in symplectic geometry}
	%
Consider two \alert{gauge-related} symplectic mfd. $(M,\omega)$ and $ (M,\widetilde{\omega})$.
	%
	\begin{center}
			\includestandalone[width=.8\textwidth]{Pictures/hyb-image_BigDiagram_symplectic}
	\end{center}
	%
	\vfill
	\begin{minipage}[t][8em][t]{\textwidth}
	\centering
	\vspace{-2em}
	\begin{tikzpicture}
		\node [draw,cloud callout,cloud puffs=50,cloud puff arc=100,blue, minimum height=10em,minimum width=35em,callout relative pointer={(-2,-2)}] (L1) {};
		\node [text width=30em,text centered] (L2) {
			\textcolor{blue}{Why should we care about this?}
			\\
			\begin{itemize}
				\item<2->[•] It's a framework for comparing gauge-related observables.
				\item<3->[•] It has a geometric interpration when $\omega$ \alert{prequantizable}.
			\end{itemize}
			\medskip
		};
	\end{tikzpicture}
	\end{minipage}	
\end{frame}
%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[fragile]{TODO}
	Details on the prequantum side.
\end{frame}
%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[t]{Scope of the talk}
		\begin{center}
		\tcbox[enhanced,frame hidden,borderline={0.5pt}{0pt}{red,dashed}]{	
			\alert{
			\faQuestionCircle \qquad
				{\bf  What happens in the (higher) $n$-plectic case?}
			\qquad \faQuestionCircle		
			}
		}
		\end{center}
		\vfill

@@

\begin{frame}[fragile]{Multisymplectic manifolds - motivations} %Fragile -->workaround tikzcd
	\begin{block}{Historical motivation}
		Mechanics: geometrical foundations of \textit{(first-order)} field theories.
		\begin{itemize}
		 \item[•] Kijowski, W. Tulczyjew \cite{Kijowski1979}; %(1979)
		 \item[•] Cariñena, Crampin, Ibort \cite{Carinena1991b};% (1991)
		 \item[•] Gotay, Isenberg, Marsden, Montgomery \cite{Gimmsy1};%(1998)
		 \\ $\cdots$
		\end{itemize}
	\end{block}
	%
	\pause
	\begin{table}
		\ifHandout
		%
		\else
		\only<2>{
		\begin{tabular}{|p{0.2\textwidth}|p{0.3\textwidth}|p{0.35\textwidth}|} 
            \hline
            \parbox[][20pt][c]{0.2\textwidth}{mechanics} & \multicolumn{2}{c|}{geometry} \\
            \hline
            \parbox[][20pt][c]{0.2\textwidth}{phase space} & symplectic manifold &  \\[.25em]
            \parbox[][20pt][c]{0.2\textwidth}{classical \\ observables} & Poisson algebra &  \\[.25em]
            \parbox[][20pt][c]{0.2\textwidth}{symmetries} &  group actions admitting comoment map &  
            \\
            \hline
  \multicolumn{1}{c}{}
            &  \multicolumn{1}{@{}c@{}}{$\underbrace{\hspace*{.3\textwidth}}_{\text{point-like particles systems}}$} 
            &  \multicolumn{1}{@{}c@{}}{}              \\
		\end{tabular}
		}
		\fi
		\onslide<3->{
		\begin{tabular}{|p{0.2\textwidth}|p{0.3\textwidth}|p{0.35\textwidth}|} 
            \hline
            \parbox[][20pt][c]{0.2\textwidth}{mechanics} & \multicolumn{2}{c|}{geometry} \\
            \hline
            \parbox[][20pt][c]{0.2\textwidth}{phase space} & symplectic manifold & multisymplectic manifold \\[.25em]
            \parbox[][20pt][c]{0.2\textwidth}{classical \\ observables} & Poisson algebra & $L_\infty$-algebra \\[.25em]
            \parbox[][20pt][c]{0.2\textwidth}{symmetries} &  group actions admitting comoment map & group actions admitting (homotopy) comomentum map
            \\
            \hline
  			\multicolumn{1}{c}{}
            &  \multicolumn{1}{@{}c@{}}{$\underbrace{\hspace*{.3\textwidth}}_{\text{point-like particles systems}}$} 
            &
            \multicolumn{1}{@{}c@{}}{$\underbrace{\hspace*{.3\textwidth}}_{\text{field-theoretic systems}}$} 
               \\
		\end{tabular}
		}
	\end{table}

@@

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[fragile]{TODO}
	Details on the GIMMSY Construction

	Mention Blohmann for the higher case
\end{frame}
%-------------------------------------------------------------------------------------------------------------------------------------------------

@@

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[fragile]{TODO}
	Details on the controversial notion

	pdv meccanico: sono misurabili?

	pdv matematico: perchè questa è preferibile a struttura di Leibniz (check che sia la stessa usata da gimsy e spagnoli)
\end{frame}
%-------------------------------------------------------------------------------------------------------------------------------------------------

@@

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}{Gauge related multisymplectic manifolds and comoment maps}
	Consider $M$ smooth mfd.
	%
	\begin{defblock}[Gauge related $n$-plectic structures]
		\bigskip
		\begin{columns}[T]
			\setlength{\belowdisplayskip}{5pt}
			\begin{column}{.50\linewidth}
				%
				\centering \it
				\onslide<2->{
				$\quad\omega,~ \tilde{\omega}~ \in \Omega^{n+1}(M)$ multisymplectic,
				}
			\end{column}	
			%
			\begin{column}{.50\linewidth}
				\centering \it
				\onslide<3->{			
				such that $\omega = \tilde{\omega} - d B$
				}
			\end{column}	
		\end{columns}	
		\bigskip	
	\end{defblock}
	%
	\pause
	\vfill
	\par\noindent\rule{\textwidth}{0.4pt}	
	\vfill
	\pause
	%
	Consider \quad $v:\mathfrak{g} \to \mathfrak{X}(M)$ preserving $\omega$ and $\tilde{\omega}$,
	%\phantom{consider}\quad $\mathcal{L}_{v_\xi}\omega=\mathcal{L}_{v_\xi}\tilde{\omega} = 0 \quad \forall \xi \in \mathfrak{g}$
	\\
	let \qquad$f: \mathfrak{g}\to L_\infty(M,\omega)$ an \emph{homotopy comoment map} ~ w.r.t. $\mathfrak{g}\circlearrowleft (M,\omega)$
	\pause
	\begin{lemblock}[Also $(M,\tilde{\omega})$ admits HCMM $(\tilde{f})$]
		\medskip
		\begin{columns}
			\begin{column}{.325\linewidth}
					\onslide<5->{
						\begin{displaymath}
							\tilde{f}_k = f_k +	
								\tikz[baseline,remember picture]{\node[rounded corners,
	                        		fill=blue!5,draw=blue!30,anchor=base]            
	            					(target) {$\mathrm{b}_k$ };
	            					}	
						\end{displaymath}
					}		
			\end{column}
			\begin{column}{.625\linewidth}	
					\onslide<5->{
						\begin{displaymath}
						%
						\begin{tikzcd}[baseline=(O.base),ampersand replacement=\&]
							|[alias=O]| 
							\tikz[baseline,remember picture]{\node[rounded corners,
	                        		fill=blue!2,draw=blue!30,align=center]            
	            					(base) {$\mathrm{b}_k$};}						
							~:\&[-3em] \Lambda^k\mathfrak{g} \ar[r]\& \Omega^{n-k}(M)
							\\[-2em]
							\& \xi_1\wedge\dots \xi_k \ar[r,mapsto] \&
							(-)^k \iota(v_{\xi_1})\dots \iota(v_{\xi_{x_k}}) B
						\end{tikzcd}		
						\end{displaymath}								
					}		
			\end{column}
		\end{columns}
		\bigskip
		\only<5->{
			\begin{tikzpicture}[overlay,remember picture]
			    	\path[->,opacity=0.3] (base.west) edge[bend left,blue](target.south east);
		    \end{tikzpicture}		
	    }
	\end{lemblock}
	%
\end{frame}
%-------------------------------------------------------------------------------------------------------------------------------------------------

>>>>

%+----------------------------------------------------------------------------+
%| SLIDES: 
%|
%| Contents:	- 60 minutes, 
%| Note: Riprovo a dare il talk dopo che a Wurzburg è andata male.
%|		 Lì ho sbagliato tutti i tempi ma non so stabilire se è stato un problema di scarsa preparazione
%|       , di farmaci, o di stress da brutte notizie sulla crioc.
%|
%|
%|
%| Author: Antonio miti
%| Place: Caprarola, VT
%| Date: 2/3/24
%+----------------------------------------------------------------------------+

%- D0cum3nt ----------------------------------------------------------------------------------------------
\documentclass[10pt,handout]{beamer}

@@

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[fragile]{A \emph{pentagonal} diagram in symplectic geometry}
	Given a \alert{symplectic mfd.} $(M,\omega)$ ...
	\vfill
	\begin{center}
		\includestandalone[width=.95\textwidth]{Pictures/Frame_Embedding_Diagram_symplectic}
	\end{center}
	\vfill
	\begin{minipage}[t][8.5em][t]{\textwidth}
		\only<1-3>{One can naturally associate:}
		\begin{itemize}
			\only<1-3>{
			\item<1-> a \alert<1>{Poisson algebra} w/ $$\{f,g\}_\omega = -\iota_{\vHam_f}\iota_{\vHam_g} \omega$$
			\item<2-> a \alert<2>{(standard twisted) Lie Algebroid};
			\item<3->[-] A Lie algebroid is a "controlled" $\infty$-dimensional Lie algebra w/
			\begin{displaymath}
					\left[\binom{x_1}{f_1},\binom{x_2}{f_2}\right]_\omega
					~=~
					\binom{[x_1,x_2]}{x_1(f_2)-x_2(f_1)-\omega(x_1,x_2)}
				\end{displaymath}
			}
			\item[]<4->
				\quad\\
				\begin{thmblock}[There exists an embedding of Lie algebras.]
					\begin{displaymath}
						\begin{tikzcd}
							\Psi~:&[-1em] (C^{\infty}(M), \{\cdot,\cdot\}_\omega) \ar[r,"\Psi"]& 
							(\Gamma(TM\oplus \mathbb{R}), [\cdot,\cdot]_\omega)
							\\[-2em]
							& f \ar[r,mapsto] & \binom{\mathscr{v}_f}{f}
						\end{tikzcd}		
					\end{displaymath}
				\end{thmblock}
		\end{itemize}
	\end{minipage}
\end{frame}
\note{}
%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[fragile]{A \emph{pentagonal} diagram in symplectic geometry}
	%
	Consider two \alert{gauge-related} symplectic mfd. $(M,\omega)$ and $ (M,\widetilde{\omega})$.
	~~ \alert{($\widetilde{\omega} = \omega - \d B$)}
	%
	\begin{center}
			\includestandalone[width=.8\textwidth]{Pictures/hyb-Frame_BigDiagram_symplectic}
	\end{center}
		\vfill
	\begin{minipage}[t][8em][t]{\textwidth}
		\begin{itemize}
			\only<3-4>{
				\item<3-> There is a natural \alert<3>{isomorphism in the Lie Alg.oids category} \emph{($B$-transformation)}
					\begin{displaymath}
						\binom{x}{f} \mapsto \binom{x}{f-\iota_x B} ~.
					\end{displaymath}~.
				\item<4-> It descends to an \alert<4>{isomorphism of Lie algebras}.
			}
			\only<6-8>{
				\item<6-> \vspace{-2em}Consider an infinitesimal \alert<6>{Hamiltonian group action} $\mathfrak{g}\curvearrowright M$ w.r.t. both $\omega$ and $\tilde{\omega}$.
				\item<7-> let be $f:\mathfrak{g} \to C^\infty(M)_\omega$ and $\tilde{f}:\mathfrak{g} \to C^\infty(M)_{\tilde{\omega}}$ two comoment map s.t.
				\begin{displaymath}
					\tilde{f}(\xi) = f(\xi) - \iota_{\underline{\xi}}B
				\end{displaymath}
				}
			\item[]						
		\end{itemize}
	\only<2>{
		\vspace{-.75em}
		\begin{center}
		\tcbox[enhanced,frame hidden,borderline={0.5pt}{0pt}{red,dashed}]{	
			\alert{
			\faQuestionCircle \qquad
				{How can we compare the two \emph{observables} algebras?}
			\qquad \faQuestionCircle		
			}
		}
		\end{center}
	}
	\only<5>{
		\vspace{-.75em}
		\begin{center}
		\tcbox[enhanced,frame hidden,borderline={0.5pt}{0pt}{red,dashed}]{	
			\alert{
			\faQuestionCircle \qquad
				{How can we close the left-hand side?}
			\qquad \faQuestionCircle		
			}
		}
		\end{center}
	}
	\only<8->{
		\vspace{-.75em}
		\tcbset{colback=white,
		colbacktitle=white,
		colframe=red!70!black,
		boxrule=1pt,
		colupper=red!70!black,
		arc=15pt,
		}
		\begin{tcolorbox}[enhanced,frame hidden,borderline={0.5pt}{0pt}{blue}]
			\color{blue}{
			\textbf{Lemma}: The central pentagon commutes!
			}
			\hfill \hyperlink{frame:whyNoVertArrow}{\color{gray}$[>>]$}%\beamerskipbutton{}}
		\end{tcolorbox}
	\vfill

	}
	\end{minipage}	
\end{frame}
%-------------------------------------------------------------------------------------------------------------------------------------------------

@@

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[fragile]{Why not a direct vertical arrow?}\label{frame:whyNoVertArrow}
	\begin{center}
			\includestandalone[width=.7\textwidth]{Pictures/Frame_BigDiagram_verticalArrow}
	\end{center}
	\vfill
	\begin{itemize}
		\item<2-> Assume exists \alert<2>{$\chi:C^\infty(M)_\omega \to C^\infty(M)_{\widetilde{\omega}}$} ~s.t. the square commutes.
				\begin{displaymath}
					\begin{cases}
						\chi(f) =& f - \iota_{\vHam_f} B
						\\
						\widetilde{\vHam}_{\chi(f)} =& \vHam_f
					\end{cases}
				\end{displaymath}
		\item<3-> Then
			\begin{align*}
				d \chi(f) &= - \iota_{\vHam_f}\omega - d \iota_{\vHam_f} B \\
				\parallel & \\
				-\iota_{\widetilde{\vHam}_{\chi(f)}} \widetilde{\omega} &= -\iota_{\vHam_f} \omega + \iota_{\vHam_f} d B
			\end{align*}
		\item<4-> I.e. $$\mathcal{L}_{\vHam_f} B = 0 ~ \forall f \in C^\infty(M) \qquad \qquad \text{\alert{contradiction!}}$$
	\end{itemize}
	\hfill \hyperlink{frame:pentagonMotivation}{\color{gray}$[<<]$}%\beamerskipbutton{}}
\end{frame}
%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[fragile]{A \emph{pentagonal} diagram in symplectic geometry}\label{frame:pentagonMotivation}
	%
	%Consider two \alert{gauge-related} symplectic mfd. $(M,\omega)$ and $ (M,\widetilde{\omega})$.
	We end up with a pentagonal diagram ...
	%
	\begin{center}
			\includestandalone[width=.8\textwidth]{Pictures/hyb-image_BigDiagram_symplectic}
	\end{center}
	%
	\vfill
	\begin{minipage}[t][8em][t]{\textwidth}
	\centering
	\vspace{-2em}
	\begin{tikzpicture}
		\node [draw,cloud callout,cloud puffs=50,cloud puff arc=100,blue, minimum height=10em,minimum width=35em,callout relative pointer={(-2,-2)}] (L1) {};
		\node [text width=30em,text centered] (L2) {
			\textcolor{blue}{Why should we care about this?}
			\\
			\begin{itemize}
				\item<2->[•] It's a framework for comparing gauge-related observables (same cohomology class).
				\item<3->[•] It has a geometric interpration when $\omega$ \alert{prequantizable}.
				\hfill \hyperlink{frame:pentagonPrequantum}{\color{gray}$[>>]$}%\beamerskipbutton{}}
			\end{itemize}
			\medskip
		};
	\end{tikzpicture}
	\end{minipage}

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[fragile]{Pentagonal diagram in the \emph{prequantizable} case}\label{frame:pentagonPrequantum}
	Assume $\omega$ is \alert{prequantizable}:
	\pause
	%
		\begin{columns}
			\begin{column}{.6\linewidth}
				\begin{itemize}
					\item<2-> $\pi:P\to M$ \small associated $S^1$ bundle;
					\item<3-> $E\in \mathfrak{X}(P)$ \small fundamental v.f. of $S^1\curvearrowright P$;
					\item<4-> $\theta\in \Omega^1(P)^{S^1}$ \small connection $1$-form  s.t. $d \theta = \pi^\ast \omega$.
				\end{itemize}
			\end{column}
			\begin{column}{.4\linewidth}
				\begin{center}
					\includestandalone[width=1\textwidth]{Pictures/Frame_prequantum}
				\end{center}	
			\end{column}
		\end{columns}
	\pause \pause \vfill
	The Lie algebra map
	\begin{displaymath}
		\big(C^\infty(M),\{\cdot,\cdot\}_\omega\big) \xrightarrow{\Psi_\omega} 
		\big(\Gamma(TM\oplus\mathbb{R}),[\cdot,\cdot]_\omega\big)
	\end{displaymath}
	%
	\vfill
	factors through the Lie algebra of \emph{\alert{infinitesimal quanto-morphisms}}
	%
	\pause
	\begin{displaymath}
		Q(P,\theta)= \left \lbrace 
			Y \in \mathfrak{X}(P) 
			~ \Big\vert ~
			\mathcal{L}_Y \theta = 0
			\right \rbrace~.
	\end{displaymath}

	\hfill \hyperlink{frame:scopeTalk}{\color{gray}$[<<]$}%\beamerskipbutton{}}
\end{frame}
%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[fragile]{Pentagonal diagram in the \emph{prequantizable} case \hfill (cont.)}
	\begin{center}
			\includestandalone[width=.8\textwidth]{Pictures/Frame_prequantumDiagram}
	\end{center}	
	\vfill
	\begin{enumerate}
		\item<2-> Start from the prequantization map (isomorphism)
					$$\textrm{Preq}_\theta: f \mapsto \vHam_f^{Hor \theta} + (\pi^\ast f ) E $$
					\hfill {\tiny ( where $Hor \theta$ is the horizontal lift);}
		\item<3-> Observe that $Q(P,\theta) \subset \mathfrak{X}^{S^1}$;
		\item<4-> By definition, $\mathfrak{X}^{S^1}= \Gamma(\textrm{at}(P))$ where $\textrm{at}(P)$ is the Atiyah Lie algebroid associated to the principal bundle $P\to M$.
		\item<5-> $\textrm{at}(P)$ is defined by the s.e.s. $0\to \mathbb{R} \to \textrm{at}(P) \to TM \to 0$,
		\\ $\theta$ provides a splitting, i.e. an isomorphism
		\begin{displaymath}
			\morphism{\sigma_\theta}{TM\oplus \mathbb{R}}{\textrm{at}(P)}
			{\binom{v}{c}}{v^{Hor \theta} + c \cdot E}~.
		\end{displaymath}
	\end{enumerate}

	\hfill \hyperlink{frame:scopeTalk}{\color{gray}$[<<]$}%\beamerskipbutton{}}
\end{frame}
%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[t]{Scope of the talk}\label{frame:scopeTalk}
		\begin{center}
		\tcbox[enhanced,frame hidden,borderline={0.5pt}{0pt}{red,dashed}]{	
			\alert{
			\faQuestionCircle \qquad
				{\bf  What happens in the (higher) $n$-plectic case?}
			\qquad \faQuestionCircle		
			}
		}
		\end{center}
		\vfill

@@

\begin{frame}[fragile]{Multisymplectic manifolds - mechanics perspective} %Fragile -->workaround tikzcd
	\label{frame:hystMS}
	\begin{block}{Historical motivation}
		Mechanics: geometrical foundations of \textit{(first-order)} field theories.
		\begin{itemize}
		 \item[•] Kijowski, W. Tulczyjew \cite{Kijowski1979}; %(1979)
		 \item[•] Cariñena, Crampin, Ibort \cite{Carinena1991b};% (1991)
		 \item[•] Gotay, Isenberg, Marsden, Montgomery \cite{Gimmsy1};%(1998)
		 \\ $\cdots$
		\end{itemize}
	\end{block}
	%
	\pause
	\begin{table}
		\ifHandout
		%
		\else
		\only<2>{
		\begin{tabular}{|p{0.2\textwidth}|p{0.3\textwidth}|p{0.35\textwidth}|} 
            \hline
            \parbox[][20pt][c]{0.2\textwidth}{mechanics} & \multicolumn{2}{c|}{geometry} \\
            \hline
            \parbox[][20pt][c]{0.2\textwidth}{phase space} & symplectic manifold &  \\[.25em]
            \parbox[][20pt][c]{0.2\textwidth}{classical \\ observables} & Poisson algebra &  \\[.25em]
            \parbox[][20pt][c]{0.2\textwidth}{symmetries} &  group actions admitting comoment map &  
            \\
            \hline
  \multicolumn{1}{c}{}
            &  \multicolumn{1}{@{}c@{}}{$\underbrace{\hspace*{.3\textwidth}}_{\text{point-like particles systems}}$} 
            &  \multicolumn{1}{@{}c@{}}{}              \\
		\end{tabular}
		}
		\fi
		\onslide<3->{
		\begin{tabular}{|p{0.2\textwidth}|p{0.3\textwidth}|p{0.35\textwidth}|} 
            \hline
            \parbox[][20pt][c]{0.2\textwidth}{mechanics} & \multicolumn{2}{c|}{geometry} \\
            \hline
            \parbox[][20pt][c]{0.2\textwidth}{phase space} & symplectic manifold & multisymplectic manifold \\[.25em]
            \parbox[][20pt][c]{0.2\textwidth}{classical \\ observables} & Poisson algebra & $L_\infty$-algebra \\[.25em]
            \parbox[][20pt][c]{0.2\textwidth}{symmetries} &  group actions admitting comoment map & group actions admitting (homotopy) comomentum map
            \\
            \hline
  			\multicolumn{1}{c}{}
            &  \multicolumn{1}{@{}c@{}}{$\underbrace{\hspace*{.3\textwidth}}_{\text{point-like particles systems}}$} 
            &
            \multicolumn{1}{@{}c@{}}{$\underbrace{\hspace*{.3\textwidth}}_{\text{field-theoretic systems}}$} 
               \\
		\end{tabular}
		}
	\end{table}		 
 	\hfill \hyperlink{frame:GIMMSY_construction}{\color{gray}$[>>]$}%\beamerskipbutton{}}

@@

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[fragile]{A multisymplectic manifold in Lagrangian Field Theory}\label{frame:GIMMSY_construction}
	\begin{center}
		\includestandalone[width=.5\textwidth]{Pictures/Frame_GIMMSY}
	\end{center}	
	\vfill

	Consider a \emph{\bf{first-order Lagrangian Field Theory}}:
	\begin{itemize}
		\item<1-> {\color{blue} Kinematics} is encoded by a {\color{blue} \emph{configuration bundle}};
		\item<2-> {\color{red} Dynamics} is encoded by a {\color{red} \emph{Lagrangian density}};
		\item<3-> The {\color{orange} multicontangent bundle} is naturally $n$-plectic with $\omega := d \theta$ and \\
		$\theta \in \Omega^n(\Lambda)$ the tautological $n$-form
		{\small
		\begin{displaymath}
			\left[ \iota_{u_1 \wedge \ldots \wedge u_n} \theta \right]_\eta 
			= \iota_{u_1 \wedge \ldots \wedge u_n} \pi^\ast \eta 
			\qquad \qquad \forall \eta \in \wedge^n T^* E \, , \: \forall u_i \in T_\eta (\wedge^n T^* E) 		
		\end{displaymath}
		}
		\item<4-> The multisymplectic $(n+1)$-form is pulled back to $J^1 E$ through the \emph{Legendre transformation} $\mathbb{F}\Lag: J^1 E \to (J^1 E)^\ostar$
    given intrinsically by
    {\small
		\begin{displaymath}
        		\Big\langle \mathbb{F}\mathcal{L}(\gamma),\gamma'\Big\rangle=
        		\mathcal{L}\Big(\gamma\Big) + \frac{ d}{ d \epsilon}\mathcal{L}\Big(\gamma +\epsilon(\gamma'-\gamma)\Big)\Bigg\vert_{\epsilon=0} \qquad \forall \gamma,\gamma' \in J^1 E
    		\end{displaymath}
    }

    %
	\end{itemize}
	%
	\vfill
	\hfill \hyperlink{frame:hystMS}{\color{gray}$[<<]$}%\beamerskipbutton{}}
\end{frame}
%-------------------------------------------------------------------------------------------------------------------------------------------------

@@

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[fragile,shrink]{Multisymplectic Observables - a controversial notion}
	\begin{block}{ Much debate about the "correct" mathematical of \emph{multisymplectic observables}}
		\begin{itemize}
			\item A crucial step for quantization schemes.
			\item Obstructed adoption of this formalism in mechanics.
		\end{itemize}	
	\end{block}		
	%
	\vspace{1.5em} \pause
	\begin{block}{ At least a second competing notion of \emph{multisymplectic observables algebra}}
		\begin{displaymath}
			Leib(M,\omega) = \Big( \Omega_{ham}^{n-1}(M,\omega), \llbracket\cdot,\cdot\rrbracket \Big)
		\end{displaymath}
		with the binary bracket 
		\begin{center}
			\includestandalone{Pictures/Equation_Leibbracket}	
		\end{center}
	\end{block}	
	\vspace{1em} \pause
	\begin{block}{Open Questions:}
		\begin{itemize}
			\item How are the two concepts related?
			\item Do they give what is physically expected to be called an \emph{measurable quantity}?
				\\
				(Folklore conjecture: No, they only give \emph{local observables})				
		\end{itemize}
	\end{block}
\end{frame}
%-------------------------------------------------------------------------------------------------------------------------------------------------

@@

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}{Gauge related multisymplectic manifolds and comoment maps}
	Consider $M$ smooth mfd.
	%
	\begin{defblock}[Gauge related $n$-plectic structures]
		\bigskip
		\begin{columns}[T]
			\setlength{\belowdisplayskip}{5pt}
			\begin{column}{.50\linewidth}
				%
				\centering \it
				$\quad\omega,~ \tilde{\omega}~ \in \Omega^{n+1}(M)$ multisymplectic,
			\end{column}	
			%
			\begin{column}{.50\linewidth}
				\centering \it
				such that $\omega = \tilde{\omega} - d B$
			\end{column}	
		\end{columns}	
		\bigskip	
	\end{defblock}
	%
	\pause
	\vfill
	\par\noindent\rule{\textwidth}{0.4pt}	
	\vfill
	%
	Consider \quad $v:\mathfrak{g} \to \mathfrak{X}(M)$ preserving $\omega$ and $\tilde{\omega}$,
	%\phantom{consider}\quad $\mathcal{L}_{v_\xi}\omega=\mathcal{L}_{v_\xi}\tilde{\omega} = 0 \quad \forall \xi \in \mathfrak{g}$
	\\
	let \qquad$f: \mathfrak{g}\to L_\infty(M,\omega)$ an \emph{homotopy comoment map} ~ w.r.t. $\mathfrak{g}\circlearrowleft (M,\omega)$
	\pause
	\begin{lemblock}[Also $(M,\tilde{\omega})$ admits HCMM $(\tilde{f})$]
		\medskip
		\begin{columns}
			\begin{column}{.325\linewidth}
					\onslide<4->{
						\begin{displaymath}
							\tilde{f}_k = f_k +	
								\tikz[baseline,remember picture]{\node[rounded corners,
	                        		fill=blue!5,draw=blue!30,anchor=base]            
	            					(target) {$\mathrm{b}_k$ };
	            					}	
						\end{displaymath}
					}		
			\end{column}
			\begin{column}{.625\linewidth}	
					\onslide<4->{
						\begin{displaymath}
						%
						\begin{tikzcd}[baseline=(O.base),ampersand replacement=\&]
							|[alias=O]| 
							\tikz[baseline,remember picture]{\node[rounded corners,
	                        		fill=blue!2,draw=blue!30,align=center]            
	            					(base) {$\mathrm{b}_k$};}						
							~:\&[-3em] \Lambda^k\mathfrak{g} \ar[r]\& \Omega^{n-k}(M)
							\\[-2em]
							\& \xi_1\wedge\dots \xi_k \ar[r,mapsto] \&
							(-)^k \iota(v_{\xi_1})\dots \iota(v_{\xi_{x_k}}) B
						\end{tikzcd}		
						\end{displaymath}								
					}		
			\end{column}
		\end{columns}
		\bigskip
		\only<4->{
			\begin{tikzpicture}[overlay,remember picture]
			    	\path[->,opacity=0.3] (base.west) edge[bend left,blue](target.south east);
		    \end{tikzpicture}		
	    }
	\end{lemblock}
	%
\end{frame}
%-------------------------------------------------------------------------------------------------------------------------------------------------
